---
title: "Machine Learning I -- STA314"
author: "Tahir Muhammad"
date: "04/10/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Tutorial 1 - KNN

Today we will conduct some basic data analysis on an different methods of Advertising data from a Company X. 
Afterwards, we will go through the K-Nearest Neighbours Algorithm in R, train the model, and illustrate it's MSE. 
Let's Get Started! 

```{r}
 #--------------------------------------------------------------
 # Data Analysis: loading data sets into R and making plots
 #--------------------------------------------------------------
# 
# read in the dataset
getwd()
df <- read.csv("/home/tahir/Downloads/Advertising.csv")
# Look at the top few rows
head(df)
```

Hi 

```{r}
 #fix(df) # take a look at data in table form
# names(df) # names of entries in df
 #$TV # values of column TV
 #TV # does not work, not in memory
 #attach(df) # make elements of res available in workspace
 #TV # now works
```



```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
